---
title: "Movies Vizualization"
output:
  rmdformats::robobook:
    highlight: default
    code_folding: hide
    self_contained: False
    md_extensions: "+emoji"
---


```{r setup, include=FALSE, dev="ragg_png"}
library(knitr)
library(ragg)
options(max.print="75")
opts_chunk$set(dev="ragg_png",
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```


# Data :floppy_disk:


Source:  [Tidy tuesday](https://github.com/rfordatascience/tidytuesday/tree/master/data/2018/2018-10-23).  
Original data source: [The numbers](https://www.the-numbers.com/).


<!-- -->

    Main data about movies such as:
    • Title
    • Production budget
    • Worldwide gross
    • Domestic gross
    • Genre
    • MPAA rating


```{r}
library(here)

source(here("scripts/read_data.R"))

data<- read_and_save_data(here("data/raw/movie_profit.csv"),here("data/clean/movie_profit.RDS"))
```


# Plots :bar_chart:

## Age ratings and genres :baby:

Relationship between movie genres and their MPAA ratings is visualised first.

```{r}
source(here("scripts/plots_small.R"))
```


```{r}
plot_1(data)
```


```{r}
plot_6(data)
```




```{r}
plot_3(data)
```

## Budgets and profit :moneybag:
 
In addition to genres/MPAA ratings, trends in movie gross and return on investment are visualised.
```{r}
plot_2(data)
```


```{r}
plot_4(data)
```

```{r}
plot_5(data)
```

# 80s deep dive :eight::zero:

The data is filtered to only include movies released in the 80s and additional analysis is done. For this deep dive budget and gross figures are adjusted for inflation :chart_with_upwards_trend:.
```{r results='hide'}
library(priceR)
data2 <- data %>%
  mutate(
    production_budget = adjust_for_inflation(production_budget, year, "US", to_date = 2019),
    worldwide_gross = adjust_for_inflation(worldwide_gross, year, "US", to_date = 2019)
  ) %>%
  filter(year %in% 1980:1989)

saveRDS(data2,here("data/clean/movie_profit_adjusted_for_inflation.RDS"))

source(here("scripts/plots_panel.R"))
```

## One-by-one {.tabset}

The plots for the deep dive are created individually.

### 1.

A small donut chart that shows the total gross by genre of the movie.

```{r}
p1 <- panel_1(data2)
p1
```

### 2.

A small bar chart to highlight the movies with the highest budget.

```{r}
p2 <- panel_2(data2)
p2
```

### 3.

"Big" chart showcasing the highest grossing movies.

```{r}
p3 <- panel_3(data2)
p3
```

### 4.

Another "big" chart showcasing movies with high budgets.

```{r}
library(svglite)
p4 <- panel_4(data2)
p4
```

## Putting it into an infographic

After creating the individual plots, they are put together into an inforgraphic.

```{r fig.width = 17, fig.height = 12}
library(patchwork)
a <- "AAAAACC
AAAAACC
AAAAACC
AAAAACC
BBBBBDD
BBBBBDD
BBBBBDD"

p3 + p4 + p1 + p2 + plot_layout(design = a) +
  plot_annotation(title = paste("80s movies",emo::ji("popcorn")),theme = theme(plot.title = element_text(size = 32, family = "Roboto Condensed")))
```


# To do :thinking:

- Compare movie production companies
(which ones make the biggest return on investment, which ones create the biggest blockbusters)
- Find which movies are sequels (do sequels make more money? what kind of movies even get sequels?)
- Find biggest box office flops
- Another deep dive?

# Code :clipboard:

```{r, code=readLines(here("scripts/plots_small.R")), eval=FALSE}

```

```{r, code=readLines(here("scripts/plots_panel.R")), eval=FALSE}

```


# Session info :information_source:

```{r}
devtools::session_info()
```

